### 2019-05-24 2-Chapters/2-Chapter/IEEE_WCNC_2018.git/IEEE_WCNC__2018__Paper__Lilian_Besson__07-17.tex
SHIT I'm going home

Our proposed \Aggr{} is detailed in Algorithm~\ref{algo:25:Aggr}.
%
\begin{small}
	\begin{figure}[h!]
		\centering
		\begin{framed}
		% Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
		% Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
		\begin{algorithm}[H]
			% XXX Input, data and output
			\KwIn{$N$ bandit algorithms, $\Alg_1, \dots, \Alg_N$, with $N \geq 2$}
			\KwIn{Number of arms, $K \geq 2$}
			\KwIn{Time horizon, $T \geq 1$, \textbf{not} used for the learning}
			\KwIn{A sequence of learning rates, $(\eta_t)_{t \geq 1}$}
			\KwData{Initial uniform distribution, $\pi^{0} = \cU([N])$}
			\KwResult{$\Alg_{\mathrm{aggr}}=\Aggr\left[\Alg_1, \dots, \Alg_N\right]$}
			% XXX Algorithm
			\For(\tcp*[f]{At every time step})
            {$t = 1, \dots, T$}{
				%
				% \tcp{First, run each algorithm $\Alg_a$}
				\For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
					$\Alg_a$ updates its internal state (e.g., \UCB{} indexes)\;
					It chooses $A(t+1)_{a} \in [K]$.
				}
				%
				% \tcp{The more algorithms have chosen arm $j$, the more probable it is to be chosen.}
				Let $p^{t+1}_j := \sum\limits_{a = 1}^{N} \pi^{t}_a \times \mathbbm{1}(\{A(t+1)_{a} = j\}), \;\forall 1\leq j \leq K$\;
				% \tcp*{Sum trusts}
				Then $\Alg_{\mathrm{aggr}}$ chooses arm $A(t+1) \sim p^{t+1}$\;
				% $\P(A(t+1)_{\mathrm{aggr}} = j) = p^{t+1}_j$
				% \tcp*{Sample once}
				%
				Give \emph{original} reward $(A(t+1), 1 - \ell_{A(t+1)}(t+1))$ to \emph{each} $\Alg_a$ (maybe \emph{not} on its chosen arm)\;
				Compute an \emph{unbiased} estimate of the loss of the trusted algorithms,$$ \ell^{t+1} = \ell_{A(t+1)}(t+1) / p^{t+1}_{A(t+1)}\;. $$
				% \tcp{Use bandit feedback to update $\pi^{t}$}
				% \tcp{Finally, use the instantaneous bandit feedback (loss $\ell_{A(t+1),t}$) to update $\pi^{t}$}
				% \For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
				\For{$a = 1, \dots, N$}{
					% \eIf{$\Alg_a$ was trusted, \ie, $A(t+1)_{a} = A(t+1)$}{
					\If{$\Alg_a$ was trusted, \ie, $A(t+1)_{a} = A(t+1)$}{
						$ \pi^{t+1}_{a} = \exp(\eta_t \ell^{t+1}) \times \pi^{t}_{a} $
						% \tcp*{More trusted}
						}%{
						% $ \pi^{t+1}_{a} = \exp(- \eta_t \ell^{t+1}) \times \pi^{t}_{a} $
						% \tcp*{Less trusted}
					% }
				}
				Renormalize the new $\pi$: $\pi^{t+1} := \pi^{t+1} / \sum_{a=1}^{N} \pi^{t+1}_{a}$.
				% \tcp*{Project it back to $\Delta_N$}
			}
			\caption{Our aggregation algorithm \Aggr.}
			\label{algo:25:Aggr}
		\end{algorithm}
		\end{framed}
	\end{figure}
\end{small}

@@

The loss estimate is unbiased in the following sense. If one had access to the rewards $r_k(t+1)$ (or the losses $\ell_k(t+1)$) for all arms $k$, the loss incurred by algorithm $a$ at time $t+1$ would be $\tilde{\ell}_{a,t+1} = \ell_{A_A(t+1)}(t+1)$. This quantity can only be observed for those algorithms for which $A_{a}^{t+1}=A(t+1)$. However, by dividing by the probability of observing this recommendation, one obtains an unbiased estimate of $\tilde{\ell}_{a,t}$. More precisely, if we define the estimate by
\begin{equation}
	\hat{\ell}_{a,t+1} = \frac{\ell_{A_A(t+1)}(t+1)}{p_{A_A(t+1)}^{t+1}} \mathbbm{1}(A_A(t+1) = A(t+1))
\end{equation}
satisfies $\mathbb{E}[\hat{\ell}_{a,t+1} | \mathcal{H}_t] = \tilde{\ell}_{a,t+1}$, for all $a$, where the expectation is taken conditionally to the history of observations up to round $t$, $\mathcal{H}_{t}$. Observe that $\tilde{\ell}_{a,t+1}=\ell^{t+1}$ for all algorithms $a$ such that $A_A(t+1)=A(t+1)$, and $\tilde{\ell}_{a,t+1}=0$ otherwise.

@@

Regarding the update of $\pi^t$, one can note that the trust probabilities are not all updated before the normalization step,
and an alternative would be to
increase $\pi_{a}$ if $A(t+1)_a = A(t+1)$ and to decrease it otherwise.
It would not be so different, as there is a final renormalization step, and empirically this variation has little impact on the performance of \Aggr{}.

>>>>

Our proposed \Aggr{} is detailed in Algorithm~\ref{algo:25:Aggr}.
%
\begin{small}
	\begin{figure}[h!]
		\centering
		\begin{framed}
		% Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
		% Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
		\begin{algorithm}[H]
			% XXX Input, data and output
			\KwIn{$N$ bandit algorithms, $\Alg_1, \dots, \Alg_N$, with $N \geq 2$}
			\KwIn{Number of arms, $K \geq 2$}
			\KwIn{Time horizon, $T \geq 1$, \textbf{not} used for the learning}
			\KwIn{A sequence of learning rates, $(\eta_t)_{t \geq 1}$}
			\KwData{Initial uniform distribution, $\pi^{0} = \cU([N])$}
			\KwResult{$\Alg_{\mathrm{aggr}}=\Aggr\left[\Alg_1, \dots, \Alg_N\right]$}
			% XXX Algorithm
			\For(\tcp*[f]{At every time step})
            {$t = 1, \dots, T$}{
				%
				% \tcp{First, run each algorithm $\Alg_a$}
				\For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
					$\Alg_a$ updates its internal state (e.g., \UCB{} indexes)\;
					It chooses $A_a(t+1) \in [K]$.
				}
				%
				% \tcp{The more algorithms have chosen arm $j$, the more probable it is to be chosen.}
				Let $p^{t+1}_j := \sum\limits_{a = 1}^{N} \pi^{t}_a \times \mathbbm{1}(\{A_a(t+1) = j\}), \;\forall 1\leq j \leq K$\;
				% \tcp*{Sum trusts}
				Then $\Alg_{\mathrm{aggr}}$ chooses arm $A(t+1) \sim p^{t+1}$\;
				% $\P(A(t+1)_{\mathrm{aggr}} = j) = p^{t+1}_j$
				% \tcp*{Sample once}
				%
				Give \emph{original} reward $(A(t+1), 1 - \ell_{A(t+1)}(t+1))$ to \emph{each} $\Alg_a$ (maybe \emph{not} on its chosen arm)\;
				Compute an \emph{unbiased} estimate of the loss of the trusted algorithms,$$ \ell^{t+1} = \ell_{A(t+1)}(t+1) / p^{t+1}_{A(t+1)}\;. $$
				% \tcp{Use bandit feedback to update $\pi^{t}$}
				% \tcp{Finally, use the instantaneous bandit feedback (loss $\ell_{A(t+1),t}$) to update $\pi^{t}$}
				% \For(\tcp*[f]{Can be parallel}){$a = 1, \dots, N$}{
				\For{$a = 1, \dots, N$}{
					% \eIf{$\Alg_a$ was trusted, \ie, $A_a(t+1) = A(t+1)$}{
					\eIf{$\Alg_a$ was trusted, \ie, $A_a(t+1) = A(t+1)$}{
						$ \pi^{t+1}_{a} = \exp(\eta_t \ell^{t+1}) \times \pi^{t}_{a} $
						\tcp*{Trusted more}
						}{
						% $ \pi^{t+1}_{a} = \exp(- \eta_t \ell^{t+1}) \times \pi^{t}_{a} $
						$ \pi^{t+1}_{a} = \pi^{t}_{a} $
						\tcp*{Do not update the trust now}
					}
				}
				Renormalize the new weights $\pi^{t+1}$: $\pi^{t+1} := \pi^{t+1} / \sum_{a=1}^{N} \pi^{t+1}_{a}$.
				% \tcp*{Project it back to $\Delta_N$}
			}
			\caption{Our algorithm \Aggr{} aggregating $\Alg_1,\dots,\Alg_N$.}
			\label{algo:25:Aggr}
		\end{algorithm}
		\end{framed}
	\end{figure}
\end{small}

@@

The loss estimate is unbiased in the following sense. If one had access to the rewards $r_k(t+1)$ (or the losses $\ell_k(t+1)$) for all arms $k$, the loss incurred by algorithm $a$ at time $t+1$ would be $\widetilde{\ell_{a,t+1}} = \ell_{A_a(t+1)}(t+1)$. This quantity can only be observed for those algorithms for which $A_{a}^{t+1}=A(t+1)$. However, by dividing by the probability of observing this recommendation, one obtains an unbiased estimate of $\widetilde{\ell_{a,t}}$. More precisely, if we define the estimate by
\begin{equation}
	\widehat{\ell_{a,t+1}} = \frac{\ell_{A_a(t+1)}(t+1)}{p_{A_a(t+1)}^{t+1}} \mathbbm{1}(A_a(t+1) = A(t+1))
\end{equation}
satisfies $\mathbb{E}[\widehat{\ell_{a,t+1}} | \mathcal{H}_t] = \widetilde{\ell_{a,t+1}}$, for all $a$, where the expectation is taken conditionally to the history of observations up to round $t$, $\mathcal{H}_{t}$. Observe that $\widetilde{\ell_{a,t+1}}=\ell^{t+1}$ for all algorithms $a$ such that $A_a(t+1)=A(t+1)$, and $\widetilde{\ell_{a,t+1}}=0$ otherwise.

@@

Regarding the update of $\pi^t$, one can note that the trust probabilities are not all updated before the normalization step,
and an alternative would be to
increase $\pi_{a}$ if $A_a(t+1) = A(t+1)$ and to decrease it otherwise.
It would not be so different, as there is a final renormalization step, and empirically this variation has little impact on the performance of \Aggr{}.
